Computational Luminance Constancy from Naturalistic Images

### 2018-09-08 Revision1/Revision1.tex
edited the TO DO list
AMA link

The Gaussian approximations for the posterior were estimated using the same training set that was used to learn the receptive fields.
Estimation performance was evaluated on a test set consisting of the 10\% of images in the dataset that were not in the training set.
For our primary results, estimation was based on six receptive fields.
The AMA analysis package is available at: \href{LuminanceConstancyAmaAnalysis
}{https://github.com/vijaysoophie/LuminanceConstancyAmaAnalysis}.

>>>>

The Gaussian approximations for the posterior were estimated using the same training set that was used to learn the receptive fields.
Estimation performance was evaluated on a test set consisting of the 10\% of images in the dataset that were not in the training set.
For our primary results, estimation was based on six receptive fields.
The AMA analysis package is available at: \href{https://github.com/BrainardLab/LuminanceConstancyAmaAnalysis}{https://github.com/BrainardLab/LuminanceConstancyAmaAnalysis}.
